Group 1: Tennis 

### 2019-12-07 Group1Prez.Rmd
update

Points – Smallest unit of measurement. Points increment from Love(0)-15-30-40-game.
Games – Games consist of 4 points each, and is won when a player reaches 4 points with at least a 2 point advantage.
Sets – A set consists of 6 games and is won by the player/team who reaches 6 games first with least a 2 point lead.
Advantage Set – If a game score of 6-6 is reached and advantage set rules are used, a player/team can only win a set with a 2 game lead.
Matches – A match is usually played as best of 3 or best of 5 sets.
Deuce – Occurs if a score of 40-40 is reached. In order to win the game, a player/team must win 2 consecutive points in order to take the game. If a player wins one point, they have advantage, but if they lose the next point, the score returns to deuce.
Tie-break game – If a game score of 6-6 is reached and tie-break set rules are used, players must play a tie-break game in order to decide who wins the set. In a tie-break game, a player/team must reach 7 points with a two point advantage to win. For the serving format of a tie-break game, player 1 serves for the first point, player 2 serves for the next two points, player 1 serves for the next two points after that, etc.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

@@

```{r cars, echo = TRUE}
summary(cars)
```

>>>>

- Point: Smallest unit of measurement (Love-15-30-40-game)

- Game: A game is one when a player reaches 4 points with at least a 2 point advantage

- Set: A set consists of 6 games and is won by the player who reaches 6 games first

- Advantage Set: If a game score of 6-6 is reached and advantage set rules are used, a player can only win a set with a 2 game lead

- Matches: Best of 3 set (for women) or 5 sets (for men)

- Tie-break game: If a game score of 6-6 is reached and tie-break set rules are used. In a tie-break game, a player/team must reach 7 points with a two point advantage to win

## Values

Things we need to know:

- Empirical probability of winning a rally on serve

- Empirical probability of winning a game on serve  \pause

Things we need to calculate:

- Theoretical probability of winning a game on serve

- Theoretical probability of winning a set

- Theoretical probability of winning a match

- Theoretical probability of winning the tie-breaker

@@

```{r, echo = TRUE}

```
